Explaining probabilistic predictions on the simplex\\with Shapley compositions

### 2024-01-17 presentation/figures/bifurctree.tex
edit presentation

\begin{tikzpicture}[scale=1.5]
  \draw (0,0) -- (1.1,1.1);
  \draw[dashed] (1.1,1.1) -- (1.4,1.4);
  \draw (1.4,1.4) -- (1.5,1.5);
  \draw (0.5,0.5) -- (1,0);
  \draw (1,1) -- (2,0);
  \draw (1.5,1.5) -- (3,0);

  \filldraw[black] (0.5,0.5) circle (0.75pt) node[anchor=south east]{$\tilde{p}_{1}$};
  \filldraw[black] (1,1) circle (0.75pt) node[anchor=south east]{$\tilde{p}_{2}$};
  \filldraw[black] (1.5,1.5) circle (0.75pt) node[anchor=south east]{$\tilde{p}_{N-1}$};

  \draw[black] (0,-0.25) node{$p_1$};
  \draw[black] (1,-0.25) node{$p_2$};
  \draw[black] (2,-0.25) node{$p_3$};
  \draw[black] (3,-0.25) node{$p_{N}$};
\end{tikzpicture}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

\begin{tikzpicture}[scale=1.1]
  \draw (0,0) -- (1.1,1.1);
  \draw[dashed] (1.1,1.1) -- (1.4,1.4);
  \draw (1.4,1.4) -- (1.5,1.5);
  \draw (0.5,0.5) -- (1,0);
  \draw (1,1) -- (2,0);
  \draw (1.5,1.5) -- (3,0);

  \filldraw[black] (0.5,0.5) circle (0.75pt) node[anchor=south east]{\color{blue}$\tilde{p}_{1}$};
  \filldraw[black] (1,1) circle (0.75pt) node[anchor=south east]{\color{magenta}$\tilde{p}_{2}$};
  \filldraw[black] (1.5,1.5) circle (0.75pt) node[anchor=south east]{\color{teal}$\tilde{p}_{N-1}$};

  \draw[black] (0,-0.25) node{$p_1$};
  \draw[white,fill=none](0,-0.25) circle (0.25);
  \draw[black] (1,-0.25) node{$p_2$};
  \draw[black] (2,-0.25) node{$p_3$};
  \draw[black] (3,-0.25) node{$p_{N}$};
\end{tikzpicture}

### 2024-01-17 presentation/figures/bifurctree2.tex
edit presentation

  \filldraw[black] (0.5,0.5) circle (0.75pt) node[anchor=south east]{\color{blue}$\tilde{p}_{1}$};
  \filldraw[black] (1,1) circle (0.75pt) node[anchor=south east]{\color{magenta}$\tilde{p}_{2}$};
  \filldraw[black] (1.5,1.5) circle (0.75pt) node[anchor=south east]{\color{teal}$\tilde{p}_{N-1}$};

  \draw[black] (0,-0.25) node{$p_1$};
  \draw[white,fill=none](0,-0.25) circle (0.25);
  \draw[black] (1,-0.25) node{$p_2$};
  \draw[black] (2,-0.25) node{$p_3$};
  \draw[black] (3,-0.25) node{$p_{N}$};
\end{tikzpicture}

>>>>

  \filldraw[black] (0.5,0.5) circle (1.5pt) node[anchor=south east]{\color{blue}\Large$\tilde{p}_{1}$};

  \filldraw[black] (1,1) circle (0.75pt) node[anchor=south east]{\color{red}$\tilde{p}_{2}$};
  \filldraw[black] (1.5,1.5) circle (0.75pt) node[anchor=south east]{\color{green}$\tilde{p}_{N-1}$};

  \draw[black] (0,-0.25) node{$p_1$};
  \draw[red,fill=none](0,-0.25) circle (0.25);
  \draw[black] (1,-0.25) node{$p_2$};
  \draw[red,fill=none](1,-0.25) circle (0.25);
  \draw[black] (2,-0.25) node{$p_3$};
  \draw[black] (3,-0.25) node{$p_{N}$};
\end{tikzpicture}

### 2024-01-17 presentation/figures/bifurctree3.tex
edit presentation

  \filldraw[black] (0.5,0.5) circle (1.5pt) node[anchor=south east]{\color{blue}\Large$\tilde{p}_{1}$};

  \filldraw[black] (1,1) circle (0.75pt) node[anchor=south east]{\color{red}$\tilde{p}_{2}$};
  \filldraw[black] (1.5,1.5) circle (0.75pt) node[anchor=south east]{\color{green}$\tilde{p}_{N-1}$};

  \draw[black] (0,-0.25) node{$p_1$};
  \draw[red,fill=none](0,-0.25) circle (0.25);
  \draw[black] (1,-0.25) node{$p_2$};
  \draw[red,fill=none](1,-0.25) circle (0.25);
  \draw[black] (2,-0.25) node{$p_3$};
  \draw[black] (3,-0.25) node{$p_{N}$};
\end{tikzpicture}

>>>>

  \filldraw[black] (0.5,0.5) circle (0.75pt) node[anchor=south east]{\color{blue}$\tilde{p}_{1}$};

  \filldraw[black] (1,1) circle (1.5pt) node[anchor=south east]{\color{red}\Large$\tilde{p}_{2}$};
  \filldraw[black] (1.5,1.5) circle (0.75pt) node[anchor=south east]{\color{green}$\tilde{p}_{N-1}$};

  \draw[black] (0,-0.25) node{$p_1$};
  \draw[black] (1,-0.25) node{$p_2$};

  \draw[red,fill=none](.5,-0.25) ellipse (0.75cm  and 0.25cm);

  \draw[black] (2,-0.25) node{$p_3$};
  \draw[red,fill=none](2,-0.25) circle (0.25);
  \draw[black] (3,-0.25) node{$p_{N}$};
\end{tikzpicture}

### 2024-01-17 presentation/main.tex
edit presentation

\documentclass{beamer}
\usetheme{Boadilla}
\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,chains}
\usetikzlibrary[calc]
\usepackage{amssymb,amsmath,mathrsfs,stmaryrd,bm,amsthm,amsfonts}
\usepackage{pgfplotstable}
\usepackage{biblatex}
\addbibresource{../paper/biblio.bib}
\renewcommand{\footnotesize}{\scriptsize}
\usepackage{pifont}
\usetikzlibrary{math}

@@

  \begin{frame}
    \frametitle{Introduction}
    \textbf{Shapley values in cooperatibe game theory}\footfullcite{shapley1953value}
    \begin{itemize}
    \item Distributes the total payoff among the players.
    \item The unique quantity respecting a set of desired axiomatic properties:
      \begin{itemize}
      \item Linearity:\\
        \begin{equation}
          \phi_{\alpha v + (1-\alpha)w}(i) = \alpha \phi_{v}(i) + (1-\alpha) \phi_{w}(i),
        \end{equation}
        for a player $i$ and two games $v$ and $w$, and for $\alpha \in [0,1]$
      \item Efficiency,
        \begin{equation}
          \sum_{i\in\mathcal{C}} \phi_{v}(i) = v (\mathcal{C}),
        \end{equation}
        (the sum of the value is equal to the total payoff)
      \item Symmetry
      \end{itemize}
    \end{itemize}
  \end{frame}

@@

          ex: The output of a softmax layer lives on a multidimensional simplex!
        \end{itemize}

@@

@@

\begin{frame}
  \frametitle{The Shapley values in machine learning}
The \textbf{value function}:
\begin{equation}
  \begin{aligned}
    v_{f,\bm{x},\text{Pr}}: 2^{\mathcal{I}} &\to \mathbb{R},\\
    S &\mapsto \mathbb{E}_\text{Pr}[f(\bm{x})\mid \bm{x}_S],
  \end{aligned}
\end{equation}
where $\mathbb{E}_{\text{Pr}}[f(\bm{x}) \mid \bm{x}_S] = \int_{\bm{x} \in \mathcal{X}}f(\bm{x})\text{Pr}(\bm{x} \mid \bm{x}_S)d\bm{x}$.
\vspace{1cm}

@@

The \textbf{contribution} of the feature indexed by $i \notin S$ in the prediction $f(\bm{x})$ given the known features indexed by $S$ is given by:
\begin{equation}
  \label{eq:contrib}
  c_{f,\bm{x},\text{Pr}}(i,\bm{X}_S) = v_{f,\bm{x},\text{Pr}}(\bm{X}_{S\cup\{i\}}) - v_{f,\bm{x},\text{Pr}}(\bm{X}_S),
\end{equation}

@@

@@

\begin{frame}
\frametitle{Compositional data analysis}

@@

@@

@@

@@

\begin{frame}
\frametitle{Discussion and conclusion}

@@

\begin{frame}
\frametitle{Thank you!!}

>>>>

\documentclass{beamer}
\usetheme{Boadilla}
\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,chains}
\usetikzlibrary[calc]
\usepackage{amssymb,amsmath,mathrsfs,stmaryrd,bm,amsthm,amsfonts}
\usepackage{mathtools}
\usepackage{pgfplotstable}
\usepackage{biblatex}
\usepackage{soul}
\addbibresource{../paper/biblio.bib}
\renewcommand{\footnotesize}{\scriptsize}
\usepackage{pifont}
\usetikzlibrary{math}

\DeclareMathOperator{\logit}{logit}
\DeclareMathOperator{\sigmoid}{sigmoid}
\DeclareMathOperator{\abs}{abs}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\llr}{llr}
\DeclareMathOperator{\lr}{lr}
\DeclareMathOperator{\ilr}{ilr}
\DeclareMathOperator{\ilrl}{ilrl}
\DeclareMathOperator{\e}{e}

@@

  \begin{frame}
    \frametitle{Introduction}
    \textbf{Shapley values in cooperative game theory}\footfullcite{shapley1953value}
    \begin{itemize}
    \item Distributes the total payoff among the players.
    \item The unique quantity respecting a set of desired axiomatic properties:
      \begin{itemize}
      \item Linearity:\\
        \begin{equation}
          \phi_{\alpha v + (1-\alpha)w}(i) = \alpha \phi_{v}(i) + (1-\alpha) \phi_{w}(i),
        \end{equation}
        for a player $i$ and two games $v$ and $w$, and for $\alpha \in [0,1]$
      \item Efficiency,
        \begin{equation}
          \sum_{i\in\mathcal{C}} \phi_{v}(i) = v (\mathcal{C}),
        \end{equation}
        (the sum of the value is equal to the total payoff)
      \item Symmetry
      \end{itemize}
    \end{itemize}
  \end{frame}

@@

          ex: The output of a softmax lives on a multidimensional simplex!
        \end{itemize}

@@

\begin{frame}{Introduction}
  \begin{center}
    The relative information between parts matter!
  \end{center}
  \begin{figure}
    \centering
\begin{tikzpicture}
\begin{axis}[
  ymin=0, ymax=55,
  yticklabel=\empty,
  xticklabel=\empty,
    minor y tick num = 3,
    area style,
    ]
    \addplot+[ybar interval,mark=no] plot coordinates { (0, 0) (5, 31) (10, 0) (15, 0) (20, 0) };
    \node[] at (axis cs:2.5,15) {\Huge ?};
    \node[] at (axis cs:12.5,15) {\Huge ?};
    \node[] at (axis cs:17.5,15) {\Huge ?};
\end{axis}
\end{tikzpicture}
  \end{figure}
\end{frame}

\addtocounter{framenumber}{-1}
\begin{frame}{Introduction}
  \begin{center}
    The relative information between parts matter!
  \end{center}
  \begin{figure}
    \centering
\begin{tikzpicture}
\begin{axis}[
  ymin=0, ymax=55,
  yticklabel=\empty,
  xticklabel=\empty,
    minor y tick num = 3,
    area style,
    ]
\addplot+[ybar interval,mark=no] plot coordinates { (0, 31) (5, 31) (10, 7) (15, 31) (20, 0) };
\end{axis}
\end{tikzpicture}
  \end{figure}
\end{frame}

\addtocounter{framenumber}{-1}
\begin{frame}{Introduction}
  \begin{center}
    The relative information between parts matter!
  \end{center}
  \begin{figure}
    \centering
\begin{tikzpicture}
\begin{axis}[
  ymin=0, ymax=55,
  yticklabel=\empty,
  xticklabel=\empty,
    minor y tick num = 3,
    area style,
    ]
\addplot+[ybar interval,mark=no] plot coordinates { (0, 16) (5, 31) (10, 0) (15, 53) (20, 0) };
\end{axis}
\end{tikzpicture}
  \end{figure}
\end{frame}

@@

\begin{frame}
  \frametitle{The Shapley values in machine learning}
The \textbf{prediction difference} (knowing only features indexed by $S$):
\begin{equation}
  \begin{aligned}
    \delta_{f,\bm{x},\text{Pr}}: 2^{\mathcal{I}} &\to \mathbb{R},\\
    S &\mapsto \mathbb{E}_\text{Pr}[f(\bm{x})\mid \bm{x}_S] - \mathbb{E}_\text{Pr}[f(\bm{x})],
  \end{aligned}
\end{equation}
where $\mathbb{E}_{\text{Pr}}[f(\bm{x}) \mid \bm{x}_S] = \int_{\bm{x} \in \mathcal{X}}f(\bm{x})\text{Pr}(\bm{x} \mid \bm{x}_S)d\bm{x}$.
\vspace{1cm}

@@

The \textbf{contribution} of the feature indexed by $i \notin S$ in the prediction $f(\bm{x})$ given the known features indexed by $S$ is given by:
\begin{equation}
  \label{eq:contrib}
  c_{f,\bm{x},\text{Pr}}(i,\bm{X}_S) = \delta_{f,\bm{x},\text{Pr}}(\bm{X}_{S\cup\{i\}}) - \delta_{f,\bm{x},\text{Pr}}(\bm{X}_S),
\end{equation}

@@

  Efficiency: $\underbrace{f(\bm{x})}_{\text{prediction}}-\underbrace{\mathbb{E}_{\text{Pr}}[f(\bm{X})]}_{\text{base value}} = \sum_{i=1}^{d} \phi_f(i),$
  \vspace{1cm}

@@

\begin{frame}{Compositional data analysis}
  \begin{minipage}{0.49\textwidth}
    \begin{figure}
      \centering
      \includegraphics[width=0.6\textwidth]{figures/basalt.jpg}
      \caption{A piece of basalt}
    \end{figure}
  \end{minipage}
    \begin{minipage}{0.5\textwidth}
      Composition:
      \begin{itemize}
      \item 35\% of pyroxene,
      \item 50\% of plagioclase,
      \item 12\% of olivine,
      \item 3\% of magnetite.  
      \end{itemize}
      \vspace{0.4cm}
      $\bm{x} = [35,50,12,3]^T$,\\
      \vspace{0.2cm}
      $\displaystyle \sum_{i} x_i = 100\%$.
  \end{minipage}
\end{frame}

\begin{frame}{Compositional data analysis}
  A composition lives on a simplex:
    \vspace{-0.3cm}
    \begin{equation}
      \mathcal{S}^N = \Big\{ \bm{x} = [x_1, x_2,\dots x_{N}]^T \in \mathbb{R}^N \mid \forall i\in\llbracket 1,N \rrbracket, x_i>0 \text{~and~} \sum_{i=1}^{N} x_i = k \Big\},
    \end{equation}
    \vspace{-0.3cm}
    \begin{minipage}{0.53\textwidth}
      \begin{figure}
        \centering
        \input{figures/simplex}
        \caption{Two dimensional simplex as the sample space of three-parts compositional data.}
      \end{figure}
    \end{minipage}
    \begin{minipage}{0.45\textwidth}
  Exemples of compositional data:
  \begin{itemize}
  \item vectors of percentages,
  \item vectors of concentrations,
  \item \textbf{discrete probability distributions} (probability simplex: $k=1$).
    \end{itemize}
    \end{minipage}    
\end{frame}

\begin{frame}{Compositional data analysis}
  \begin{center}
    {\large
      \textbf{The Aitchison geometry of the simplex} gives to the simplex an\\
      \textbf{Euclidean vector space} structure.
    } \footfullcite{aitchison1986statistical,aitchison2001}\\
  \end{center}
  \vspace{0.5cm}
  {\footnotesize
    $\bm{x},\bm{y} \in \mathcal{S}^N$ and $\alpha \in \mathbb{R}$,
  \begin{itemize}
\item perturbation: $\bm{x}\oplus \bm{y} = \mathcal{C}\left([x_1y_1,\dots x_{N}y_{N}]\right)$,
    \item powering: $\alpha \odot \bm{x} = \mathcal{C}\left([x_{1}^{\alpha},\dots x_{N}^{\alpha}]\right)$,
    \item inner product: $\displaystyle \langle \bm{x},\bm{y} \rangle_a = \frac{1}{2N}\sum_{i=1}^{N} \sum_{j=1}^{N} \log \frac{x_i}{x_j}\log \frac{y_i}{y_j}$
  \end{itemize}
  where, $\mathcal{C}\left(\bm{x} \right) = \left[ \frac{x_1}{\lVert \bm{x} \rVert_1}, \frac{x_2}{\lVert \bm{x} \rVert_1} ,\dots \frac{x_N}{\lVert \bm{x} \rVert_1} \right]^T$ is the \emph{closure} operator.
  }
\end{frame}

\begin{frame}{Compositional data analysis}

  \textbf{Cartesian coordinate system and the ILR transformation}
\begin{equation}
    \tilde{\bm{p}}=\ilr(\bm{p}) = \left[\underbrace{\langle \bm{p}, \bm{e}^{(1)} \rangle_a}_{\color{blue} \tilde{\bm{p}}_1} , \underbrace{\langle \bm{p}, \bm{e}^{(2)} \rangle_a}_{\color{magenta} \tilde{\bm{p}}_2},\dots \underbrace{\langle \bm{p}, \bm{e}^{(N-1)} \rangle_a}_{\color{teal} \tilde{\bm{p}}_{N-1}}  \right]^T \in \mathbb{R}^{N-1}.
  \end{equation}
  where $\{\bm{e}^{(i)}\}_{1\leq i \leq N}$ forms an \emph{Aitchison} orthonormal basis on the simplex\footfullcite{egozcue2003isometric}.
  \begin{figure}
    \begin{minipage}{0.39\textwidth}
      \centering
      \input{figures/bifurctree}
    \end{minipage}
    \begin{minipage}{0.6\textwidth}
      \small
      \begin{equation}
        \tilde{p}_i = \langle \bm{p}, \bm{e}^{(i)} \rangle_a = \frac{1}{\sqrt{i\,(i+1)}} \log \left( \frac{\prod\limits_{j = 1}^{i}p_j}{(p_{i+1})^{i}} \right).
      \end{equation}
    \end{minipage}
    \caption{Bifurcating tree corresponding to the orthonormal basis obtained with the Gram-Schmidt procedure.}
    \label{fig:bifurctree}
  \end{figure}
\end{frame}

@@

  \begin{center}
    \large
    Use the Aitchison geometry to extend the concept of Shapley value to the simplex for explaining multidimensional probabilistic predictions.
  \end{center}
  \vspace{1cm}
\pause
  We want to explain a prediction $\bm{f}(\bm{x}) \in  \mathcal{S}^N$, where $\bm{f}:\mathcal{X}\to \mathcal{S}^N$ is the learned model.
\begin{figure}
  \centering
  \begin{tikzpicture}
  \node [draw,
	minimum width=1cm,
	minimum height=1cm
        ]  (model) {$\bm{f}$};
        \node [left=1cm of model] (x) {$\bm{x}$};
        \node [right=1cm of model] (pred) {\begin{tabular}{c}$\bm{f}(\bm{x})\in \mathcal{S}^N$\\\scriptsize $(N-1)$-dimensional\\\scriptsize probabilistic prediction\end{tabular}};
        \draw[-stealth] (x.east) -- (model.west);
        \draw[-stealth] (model.east) -- (pred.west);
      \end{tikzpicture}
    \end{figure}

    We rewrite the \textbf{prediction difference} and the \textbf{contribution} as follows:
    \begin{itemize}
      \pause
    \item \begin{equation}
        \begin{aligned}
          \bm{\delta}_{\bm{f},\bm{x},\text{Pr}}: 2^{\mathcal{I}} &\to \mathcal{S}^N,\\
          S &\mapsto \mathbb{E}^{\mathcal{A}}_\text{Pr}[\bm{f}(\bm{x})\mid \bm{x}_S] \ominus \mathbb{E}^{\mathcal{A}}_\text{Pr}[\bm{f}(\bm{x})],
        \end{aligned}
      \end{equation}
      \pause
      \item \begin{equation}
        \bm{c}_{\bm{f},\bm{x},\text{Pr}}(i,\bm{X}_S) = \bm{\delta}_{\bm{f},\bm{x},\text{Pr}}(\bm{X}_{S\cup\{i\}}) \ominus \bm{\delta}_{\bm{f},\bm{x},\text{Pr}}(\bm{X}_S),
      \end{equation}
    \end{itemize}
where $\bm{a}\ominus\bm{b}$ is the perturbation $\bm{a} \oplus \left( (-1)\odot \bm{b}\right)$ which correspond to a substraction between compositions $\bm{a}$ and $\bm{b}$, and where:

\begin{frame}
  \frametitle{Shapley composition on the simplex}
  The Shapley quantity expressing the contribution of the $i$th feature on a prediction can simply be expressed on the simplex as the composition $\bm{\phi}(i)$ given by:
\begin{equation}
  \bm{\phi}_{\bm{f},\bm{x},\text{Pr}}(i) = \frac{1}{d!} \odot \underset{\pi}{\bigoplus}\bm{c}_{\bm{f},\bm{x},\text{Pr}}(i,\pi^{<i}_{\bm{X}}).
\end{equation}
We call this quantity {\large\textbf{Shapley composition}}.\\
It lives on the probability simplex.
\vspace{0.5cm}

\pause
It is:
\begin{itemize}
\item Linear 
\item Efficient: $\underset{i=1}{\overset{d}\bigoplus} \bm{\phi}_{\bm{f}}(i) = \bm{f}(\bm{x}) \ominus \mathbb{E}^{\mathcal{A}}_{\text{Pr}}[\bm{f}(\bm{X})]$
\item Symmetric
\end{itemize}

@@

\begin{frame}
\frametitle{Explaining a prediction with Shapley compositions}
\framesubtitle{Visualizations in the isometric-log-ratio space}

We can visualize the Shapley compositions in the isometric-log-ratio space.
\begin{figure}
  \centering
  \input{figures/prob_simplex}
  \caption{Isometric-log-ratio transformation of the $2$-dimensional simplex (basis obtained with the Gram-Schmidt procedure)}
\end{figure}
where $\tilde{p}_1 = \frac{1}{\sqrt{2}} \log \frac{p_1}{p_2}$ and $\tilde{p}_2 = \frac{1}{\sqrt{6}} \log \frac{p_1p_2}{p_3^2}$.
\end{frame}

\begin{frame}
\frametitle{Explaining a prediction with Shapley compositions}
\framesubtitle{Visualizations in the isometric-log-ratio space}

And with more classes?
\vspace{0.2cm}

We can still visualize subspaces.
\pause
\begin{figure}
  \centering
  \input{../paper/bifurctree1}
  \caption{Bifurcation tree used in our $10$-classes digit recognition task.}
\end{figure}
\end{frame}

\begin{frame}
  \frametitle{Explaining a prediction with Shapley compositions}
  \framesubtitle{Histograms}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{../paper/figures/3classes/histo.png}
    \caption{Shapley compositions visualized as histograms
for the Iris classification example}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Explaining a prediction with Shapley compositions}
  \framesubtitle{Histograms}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{../paper/figures/moreclasses/histo.png}
    \caption{Shapley compositions visualized as histograms for the seven classes digit recognition example.}
  \end{figure}
\end{frame}

@@

  \begin{center}
    Use the geometrical tools!
  \end{center}
  \vspace{0.2cm}

  We can summarize an explanation with:
  \begin{itemize}
  \item The norms of the Shapley compositions,
  \item Angles between them,
  \item And projection on the class-compositions.
  \end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Discussion and conclusion}
Summarize:
\begin{itemize}
\item We proposed an extention of the concept of Shapley value for explaination in a multiclass setting
\pause
\item Shapley composition,
\pause
\item \st{scalar} \textbf{distribution/composition} living on the simplex
  \pause
\item Visualisations in the ILR space, or as histograms,
  \pause
  \item Computation of norms, angles and projections.
\end{itemize}

\pause
\vspace{0.2cm}
Future work:
\begin{itemize}
\item The literature about Shapley value is prolific,
\pause
\item Axiomatic formulation and uniqueness...
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Thank you!!}
\begin{figure}\centering
  \includegraphics[width=0.6\linewidth]{bowling.JPG}
\end{figure}
